---
title: "p8105_hw5_sc4636"
author: "Cui Sitong (sc4636)"
date: "11/7/2019"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

* replacing missing values

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

function_na = function(x) {
  
  if (is.numeric(x)) {
    replace_na(
      x, mean(x, na.rm = TRUE)
    )
  } else if (is.character(x)) {
    replace_na(
      x, "virginica"
    )
  }
  
}

iris_na_replaced = map_df(iris_with_missing, function_na)
```

## Problem 2

* import and tidy data

```{r}
name = list.files(path = "./data")
data = name %>% map_df(~read_csv(file.path("data", .)))
raw = cbind(name, data)

cleaned = raw %>% 
  mutate(name = str_remove(name, ".csv")) %>% 
  separate(name, into = c("arm", "id"), sep = "_") %>% 
  pivot_longer(week_1:week_8, names_to = "week", names_prefix = "week_",
               values_to = "obs") %>% 
  mutate_if(is.character, as.factor)
```

* spaghetti plot

```{r}
arm_lab = c(con = "Control arm", exp = "Experimental arm")

cleaned %>% 
  ggplot(aes(x = week, y = obs, group = id)) +
  geom_line(aes(color = id)) +
  labs(
    title = "Observations on each subject over time",
    x = "Week",
    y = "Observations",
    color = "Subject ID"
  ) +
  facet_grid(~arm,
             labeller = labeller(arm = arm_lab))
```

The longitudinal study traced 20 subjects, who were divided into control and experimental arm for 8 weeks. In week 1, observations in both arms ranged between -1.25 and 3.75 with a wider distribution in experimental arm compared to control arm. By the end of the study, observations in control arm still ranged between -1.25 and 2.5 while ranged between 2.5 and 7.5 in experimental arm. Both groups had oscillated observations. However, a steady trend was observed in control arm as time passed by while an increasing trend was observed in experimental arm.

## Problem 3

```{r power analysis}

```










