---
title: "p8105_hw5_sc4636"
author: "Cui Sitong (sc4636)"
date: "11/7/2019"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

* replacing missing values

```{r problem 1}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

function_na = function(x) {
  
  if (is.numeric(x)) {
    replace_na(
      x, mean(x, na.rm = TRUE)
    )
  } else if (is.character(x)) {
    replace_na(
      x, "virginica"
    )
  }
  
}

iris_na_replaced = map_df(iris_with_missing, function_na)
```

## Problem 2

* import and tidy data

```{r tidy data}
name = list.files(path = "./data")
data = name %>% map_df(~read_csv(file.path("data", .)))
raw = cbind(name, data)

cleaned = raw %>% 
  mutate(name = str_remove(name, ".csv")) %>% 
  separate(name, into = c("arm", "id"), sep = "_") %>% 
  pivot_longer(week_1:week_8, names_to = "week", names_prefix = "week_",
               values_to = "obs") %>% 
  mutate_if(is.character, as.factor)
```

* spaghetti plot

```{r plot}
arm_lab = c(con = "Control arm", exp = "Experimental arm")

cleaned %>% 
  ggplot(aes(x = week, y = obs, group = id)) +
  geom_line(aes(color = id)) +
  labs(
    title = "Observations on each subject over time",
    x = "Week",
    y = "Observations",
    color = "Subject ID"
  ) +
  facet_grid(~arm,
             labeller = labeller(arm = arm_lab))
```

The longitudinal study traced 20 subjects, who were divided into control and experimental arm for 8 weeks. In week 1, observations in both arms ranged between -1.25 and 3.75 with a wider distribution in experimental arm compared to control arm. By the end of the study, observations in control arm still ranged between -1.25 and 2.5 while ranged between 2.5 and 7.5 in experimental arm. Both groups had oscillated observations. However, a steady trend was observed in control arm as time passed by while an increasing trend was observed in experimental arm.

## Problem 3

* Generate datasets with $\hat {\beta_1}$ and p-value

```{r power analysis}
n = 30
beta0 = 2
sd = sqrt(50)

set.seed(10)

sim_reg = function(beta1) {
  
  sim_data = tibble(
    x = rnorm(30),
    y = beta0 + beta1 * x + rnorm(30, 0, sd)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  broom::tidy(ls_fit)
  
}

sim_result_0 = 
  rerun(10000, sim_reg(0)) %>% 
  bind_rows %>% 
  filter(term == "x") %>% 
  select(estimate, p.value)

sim_result = 
  tibble(beta1 = c(1:6)) %>% 
  mutate(
    output_lists = map(.x = beta1, ~rerun(10000,  sim_reg(beta1 = .x))),
    estimate_dfs = map(output_lists, bind_rows)
  ) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs) %>% 
  filter(term == "x") %>% 
  select(beta1, estimate, p.value)
```

* Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of β1 on the x axis. Describe the association between effect size and power.

```{r}
power_pl = sim_result %>%
  mutate(reject = if_else(p.value < 0.05, 1, 0)) %>% 
  group_by(beta1) %>% 
  summarise(power = mean(reject)) %>% 
  ggplot(aes(x = beta1, y = power)) +
  geom_point() +
  geom_line() +
  labs(
    title = "Power with different effect size",
    x = "Effect size",
    y = "Power"
  )
power_pl
```


```{r}
sim_result %>% 
  group_by(beta1) %>% 
  summarise(ave_estimate = mean(estimate)) %>% 
  ggplot(aes(x = beta1, y = ave_estimate)) +
  geom_point()

sim_result %>% 
  filter(p.value < 0.05) %>% 
  group_by(beta1) %>% 
  summarise(ave_estimate_rejected = mean(estimate)) %>% 
  ggplot(aes(x = beta1, y = ave_estimate_rejected)) +
  geom_point()
```










